\textbf{\large Acknowledgements}\\


We would like to express our heartfelt gratitude to the following individuals, organizations, and entities who have contributed to the completion of our graduation project:

\begin{itemize}
    \item Alexandria University, Faculty of Engineering, for providing the necessary resources and environment conducive to learning and research.
    \item Dr. Mohamed Moselhy, our supervisor, for his invaluable guidance, support, and expertise throughout this project.
    \item The developers and contributors of the following software libraries and tools: PyQt5, TensorFlow, NumPy, OpenCV, Qt. These tools have been instrumental in the implementation and success of our project.
    \item The authors of the Tacotron paper, whose innovative work laid the foundation for our exploration into speech synthesis.
    \item AI Forever for the T5 Large model, which significantly enhanced the quality and efficiency of our natural language processing tasks.
    \item The institute supporting the visually impaired in the Faculty of Commerce at Alexandria University, especially for providing us with essential Braille materials. These materials enabled us to construct a comprehensive Braille characters dataset, contributing significantly to our research.
    \item Our team members, whose dedication, collaboration, and diverse skills have been pivotal in every phase of this project. Each team member's contribution has been essential to our success.
    \item Our friends and families, for their unwavering support, understanding, and encouragement throughout our academic journey.
\end{itemize}

\textit{We extend our sincere appreciation to everyone who has been part of this collective effort. Your contributions have made a lasting impact.}

