% Hide this section from the TOC
\addtocontents{toc}{\protect\setcounter{tocdepth}{-1}}

\patchcmd{\thebibliography}{\section*}{\section}{}{}

% Suppress the section number for the References section
\renewcommand\thesection{} 

% Now we need a bibliography:
\begin{thebibliography}{99}

\bibitem{falcon2005}
Falcón, N., Travieso, C., Alonso, J., \& Ferrer, M. (2005). 
 Image Processing Techniques for Braille Writing Recognition. 
 In \textit{Proceedings of the International Conference on Image Analysis and Recognition} (pp. 379-385). Springer. \url{https://doi.org/10.1007/11556985_49}

    \bibitem{antonacopoulos2004}
    Antonacopoulos, A., \& Bridson, D. (2004). 
    A Robust Braille Recognition System. 
    In \textit{Document Analysis Systems VI} (pp. 533–545). Springer.

    \bibitem{al-salman2007}
    Al-Salman, A., AlOhali, Y., AlKanhal, M., \& AlRajih, A. (2007). 
    An Arabic Optical Braille Recognition System. 
    In \textit{Proceedings of the International Conference on Document Analysis and Recognition}.

    \bibitem{isayed2015}
    Isayed, S., \& Tahboub, R. (2015). 
    A Review of Optical Braille Recognition. 
    In \textit{Proceedings of the International Workshop on Systems, Signal Processing and their Applications} (pp. 1-5). IEEE. \url{https://doi.org/10.1109/WSWAN.2015.7210343}

    \bibitem{chamalee2016}
    Chamalee, W., Srilal, N., Athapaththu, H., \& Ranathunga, L. (2016). 
    Novel Segmentation Method for Optical Braille Character Identification. 
    In \textit{Proceedings of the International Conference on Advances in ICT for Emerging Regions}.

    \bibitem{ovodov2020}
    Ovodov, I. (2020). 
    Optical Braille Recognition Using Object Detection CNN. 
    In \textit{Proceedings of the International Conference on Pattern Recognition and Image Analysis}.

    \bibitem{kausar2021}
    Kausar, T., Sajjad, M., Kausar, A., Lu, Y., Muhammad, W., \& Ashraf, M. (2021). 
    Deep Learning Strategy for Braille Character Recognition. 
    \textit{IEEE Access}, \textit{PP}, 1-1. \url{https://doi.org/10.1109/ACCESS.2021.3138240}

    \bibitem{shokat2022}
    Shokat, S., Riaz, R., Rizvi, S., Khan, I., \& Paul, A. (2022). 
    Characterization of English Braille Patterns Using Automated Tools and RICA Based Feature Extraction Methods. 
    \textit{Sensors}, \textit{22}(5), 1836. \url{https://doi.org/10.3390/s22051836}

    \bibitem{elmi2002}
    Elmi, M., \& Evens, M. (2002). 
    Spelling Correction Using Context. 
    In \textit{Proceedings of the Conference on Computational Linguistics} (pp. 1-6). \url{https://doi.org/10.3115/980451.980906}

    \bibitem{arik2017}
    Arik, S., Chrzanowski, M., Coates, A., Diamos, G., Gibiansky, A., Kang, Y., Li, X., Miller, J., Raiman, J., Sengupta, S., \& Shoeybi, M. (2017). 
    Deep Voice: Real-time Neural Text-to-Speech. 
    In \textit{Proceedings of the International Conference on Machine Learning}.

    \bibitem{wang2017}
    Wang, Y., Skerry-Ryan, R.J., Stanton, D., Weiss, R., Jaitly, N., Yang, Z., Xiao, Y., Chen, Z., Bengio, S., Le, Q., Agiomyrgiannakis, Y., Clark, R., \& Saurous, R. (2017).     Tacotron: Towards End-to-End Speech Synthesis.      In \textit{Proceedings of the Annual Conference of the International Speech Communication Association} (pp. 4006-4010). \url{https://doi.org/10.21437/Inters    peech.2017-1452}

    \bibitem{ritchings}
    Ritchings, R., \& Antonacopoulos, A., \& Drakopoulos, D. 
    Analysis of Scanned Braille Documents. 
    In \textit{Proceedings of the International Conference on Document Analysis and Recognition}.

    \bibitem{afb}
    American Foundation for the Blind. 
    \textit{What is Braille?}. Retrieved from \url{https://afb.org/blindness-and-low-vision/braille/what-braille}

    \bibitem{canny}
    Canny Algorithm. 
    Retrieved from \url{https://www.educative.io/answers/what-is-canny-edge-detection}
    
    \bibitem{kaggle}
    Kaggle dataset. 
    Retrieved from \url{https://www.kaggle.com/datasets/shanks0465/braille-character-dataset}

    \bibitem{cnn}
    Convolutional Neural Network. 
    Retrieved from \url{https://towardsdatascience.com/convolutional-neural-networks-explained-9cc5188c4939}

    \bibitem{contextualSpellCheck}
    Python’s ‘contextualSpellCheck’ Package. 
    Retrieved from \url{https://spacy.io/universe/project/contextualSpellCheck}

    \bibitem{t5}
    Pre-trained ‘T5-large-spell’ Model. 
    Retrieved from \url{https://huggingface.co/ai-forever/T5-large-spell}

    \bibitem{opencv}
    Open source computer vision. 
    Retrieved from \url{https://docs.opencv.org/4.x/}
    
\end{thebibliography}

\noindent

\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
